Division and Factorization of p-Adic Polynomials

### 2016-01-22 polynomials/muldivfact.tex
Updating abstract

\begin{abstract}
We study two important operations on polynomials defined over complete 
discrete valuation fields (\emph{e.g.} $\Q_p$ or $k((t))$ for a 
field $k$), namely Euclidean division and factorization. We consider 
notably the question of computing slope factorizations and design a new 
simple and efficient algorithm based on Newton iteration to solve it.
One of its main feature consists in avoiding working over an extension 
of the base field.
We constantly pay particular attention to stability: we design several
precision models, compare them and always discuss optimality.
\end{abstract}

>>>>

\begin{abstract}
We study two important operations on polynomials defined over complete 
discrete valuation fields: Euclidean division and factorization. In particular,
we design a simple and efficient algorithm for computing slope factorizations,
based on Newton iteration.  One of its main features is that we avoid working
over an extension of the base field.
We pay particular attention to stability, and analyze the behavior
of the algorithm using several precision models.
\end{abstract}
